Kamala Harris Rises as the 2024 Election Front Runner: A Poll-of-Polls Forecast

### 2024-10-22 paper/paper.qmd
polling data updates to a more recent one

(Data last updated on [Day] [Month] 2024.) - [!!! MODIFY AT FINAL !!!]

@@

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (15971 observations, based on dataset available at Oct 21, 22:00). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.

>>>>

(Data last updated on 22 Oct 2024.) - [!!! MODIFY AT FINAL !!!]

@@

The original dataset sourced from FiveThirtyEight [@fivethirtyeight2024] aggregates a wide range of poll results (16012 observations, based on dataset available at Oct 22, 13:00). The polls conducted by various polling organizations capture voter preferences by taking a representative sample of the electorate and asking for the voters' candidate of choice. Surveys were conducted at the state and national levels, providing the wide perspective on public feelings across the country.
